 

### 2020-12-04 doc/manuscript/Dow_manuscript.Rmd
Formatted mean growth parameters table
moved  mean growth parameters table to tables. Rmd, formatted nicely

Metal dendrometer bands installed on *99-145* and *700-755* trees within the SCBI and Harvard Forest ForestGEO plots, respectively, were measured with a digital caliper approximately every 1-2 weeks within the growing season from 2011-2020 and 1998-2003, respectively. The number of bands measured at each site fluctuated somewhat as trees were added or dropped (e.g., because of tree mortality) from the census (Table `r sample_size_by_year`) *(tags_per_year_preclean in data folder)*. Across years, the number of bands sampled averaged *~135* at SCBI and  *~717* at Harvard Forest. At SCBI, four species were sampled including two diffuse-porous (Lirodendron tulipfera and Fagus grandafolia) and two ring-porous (Quercus rubra and Quercus alba) species. At Harvard Forest, eleven species were sampled including eight diffuse-porous and three ring-porous (Table `r species_table`)*(bands_bySP csv's in data folder)*.

@@

\newpage
```{r mean_growth_parameters_table,  eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)
mean_growth_parameters <- read.csv("tables_figures/mean_growth_parameters.csv",stringsAsFactors = FALSE, check.names = FALSE)
knitr::kable(mean_growth_parameters) 
```

>>>>

Metal dendrometer bands installed on *99-145* and *700-755* trees within the SCBI and Harvard Forest ForestGEO plots, respectively, were measured with a digital caliper approximately every 1-2 weeks within the growing season from 2011-2020 and 1998-2003, respectively. The number of bands measured at each site fluctuated somewhat as trees were added or dropped (e.g., because of tree mortality) from the census (Table `r sample_size_by_year`) *(tags_per_year_preclean in data folder)*. Across years, the number of bands sampled averaged *~135* at SCBI and  *~717* at Harvard Forest. At SCBI, four species were sampled including two diffuse-porous (Lirodendron tulipfera and Fagus grandafolia) and two ring-porous (Quercus rubra and Quercus alba) species. At Harvard Forest, eleven species were sampled including eight diffuse-porous and three ring-porous (Table `r species_table`).

@@

```{r mean_growth_parameters_table, out.width="100%", echo=FALSE, fig.align="center"}
knitr::include_graphics("tables_figures/mean_growth_parameters_table.png")
```

### 2020-12-04 doc/manuscript/tables_figures/tables.Rmd
Formatted mean growth parameters table
moved  mean growth parameters table to tables. Rmd, formatted nicely

kable(hypothesis_table, col.names = c("Hypotheses and Specific Predictions", "RP", "DP","RP", "DP", "Results"), caption = "Table 1. Table of hypotheses and associated specific predictions, whether each was supported ('yes'; signficant at p<0.05), rejected ('no'; opposite trend signficant at p<0.05), or found insigificant ('n.s.'; no significant correlation), and display items showing the results. 'RP' and 'DP' refer to ring- and diffuse- porous species, respectively.", format = "latex", booktabs = TRUE,  escape = F)%>%
  #column_spec(1, width = "4cm") %>%
  add_header_above(c(" ", "SCBI" = 2, "Harvard"=2, " " )) %>%
  pack_rows("Warmer early springs result in earlier stem growth and longer growing seasons", 1, 5, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Maximum growth rates are independent of early spring temperatures.", 6, 6, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Annual stem growth responds positively to warmer spring temperatures.", 7, 8, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) %>%

@@

>>>>

kable(hypothesis_table, col.names = c("Hypotheses and Specific Predictions", "RP", "DP","RP", "DP", "Results"), caption = "Table 1. Table of hypotheses and associated specific predictions, whether each was supported ('yes'; signficant at p<0.05), rejected ('no'; opposite trend signficant at p<0.05), or found insigificant ('n.s.'; no significant correlation), and display items showing the results. 'RP' and 'DP' refer to ring- and diffuse- porous species, respectively.", format = "latex", booktabs = TRUE,  escape = F)%>%
  #column_spec(1, width = "4cm") %>%
  add_header_above(c(" ", "SCBI" = 2, "Harvard Forest"=2, " " )) %>%
  pack_rows("Warmer early springs result in earlier stem growth and longer growing seasons", 1, 5, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Maximum growth rates are independent of early spring temperatures.", 6, 6, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("Annual stem growth responds positively to warmer spring temperatures.", 7, 8, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) %>%

@@

\newpage
```{r mean_growth_parameters_table,  eval=TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
mean_growth_parameters <- read.csv("mean_growth_parameters.csv",  col.names = c("", "ring","diffuse","ring", "diffuse"), stringsAsFactors = FALSE, check.names = FALSE)
kable(mean_growth_parameters, caption = "Table 3. Summary of parameters describing the phenology and rate of growth for ring- and diffuse- porous species at SCBI and Harvard Forest. ",  format = "latex", booktabs = TRUE,  escape = F) %>%
add_header_above(c(" ",  "SCBI" = 2, "Harvard Forest"=2 )) %>%
    column_spec(1, width = "4cm") %>%
kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```
